Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-09-25 paper_fse_acm/main.tex
update table formatting.tex

%\begin{tabular}{l|r|rr|rr}
% ---------------- C++/Java/Rust table UM Only--------------------------
\begin{table}[hbtp]
\centering
%\captionsetup{justification=centering}
\footnotesize
\caption{Regex vs. Comby for C++ (top), Java (middle), and Rust (bottom). LOC describes the project files considered. Muts. is total number of mutants generated for those files. Invalid mutants are those that don't compile.}
\label{tab:table_cpp1javarust}

@@

\begin{table}[hbtp]
\centering
\small 
\caption{Regex vs. Comby for Python. LOC describes the project files
  considered. Muts. is total number of mutants generated for those
  files.  Invalid mutants are ones that fail module load (e.g., due
  to imbalanced parenthesis, bad indentation, or similar problems).  We can use TCE to check for redundant Python mutants, shown under ``Red.''}
\label{tab:table_python1}
\begin{varwidth}{.9\columnwidth}
\begin{tabularx}{\linewidth}{l|r|rcrr|rcrr}
\toprule
\toprule
                 &                 & \multicolumn{4}{c|}{\textbf{Regex}}             &\multicolumn{4}{c}{\textbf{Comby}}  \\[1ex]
\textbf{Project} & \textbf{LOC}    & \textbf{Muts.} & \textbf{Red.}  & \textbf{\% Valid} & \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{Muts.} & \textbf{Red.}   &  \textbf{\% Valid} & \makecell{\textbf{Mut.} \\ \textbf{Score}}\\\midrule
keract           & 402             & 3984  & 729   & 41.53\% & 0.28           & 3067  & 533    & 47.96\%    & 0.26\\
dtw              & 118             & 2106  & 567   & 46.20\%    & 0.52           & 1835  & 639    & 47.19\%  & 0.55 \\
notion-          & \mr{2}{189}     & \mr{2}{1038}  & \mr{2}{82}    & \mr{2}{18.89\%}   & \mr{2}{0.57}         & \mr{2}{1019}  & \mr{2}{122}    & \mr{2}{19.23\%} & \mr{2}{0.60}  \\
sdk-py           & & & & & & \\[0.5ex]
atlassian-       & \mr{2}{236}      & \mr{2}{1511}  & \mr{2}{207}   & \mr{2}{19.99\%}    & \mr{2}{0.64}        & \mr{2}{1319}  & \mr{2}{351}    & \mr{2}{25.25\%} & \mr{2}{0.62}  \\
python-api       & & & & & & \\[0.5ex]
ESD              & 698             & 6268  & 1642  & 29.46\%    & 0.07           & 3874  & 614    & 44.18\% & 0.07\\
fiber            & 358             & 1565  & 163   & 31.08\% & 0.62           & 1466  & 241    & 31.24\% & 0.64\\\bottomrule
\end{tabularx}
\begin{tabularx}{\linewidth}{Xllrrrrrrr}
                  && &  \textbf{Red.}     & \textbf{Valid}  & \textbf{Invalid}  & \textbf{\% Valid} &\textbf{Mut. Score}\\\midrule
\multirow{4}{*}{\textbf{Overall}} & \multirow{2}{*}{Regex} & Mean &  565.00 & 913.00 & 1267.33 & 31.19\%  & 0.45\\
    &   &  Std.Dev. & 584.79  & 708.93 & 813.35 & 11.06\%  & 0.23\\
 & \multirow{2}{*}{Comby} & Mean & 416.67 & 839.33 & 840.67 & 35.84\% & 0.46\\
  &   &  Std.Dev. &  211.62 & 628.79 & 418.99 & 12.28\%  & 0.24 \\\bottomrule
\end{tabularx}
\end{varwidth}
\end{table}

@@

\begin{table}[htbp]
\centering
\caption{Python (Our Implementation vs. Mutmut vs. CosmicRay)}
\label{tab:table_python2}
\small
\begin{tabular}{l|rrr|rrr|rrr}
\toprule
                 & \mc{3}{c|}{\textbf{Comby}}   & \mc{3}{c|}{\textbf{Mutmut}} & \mc{3}{c}{\textbf{CosmicRay}} \\
\textbf{Project} & \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv}
& \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv} 
& \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv} \\ \midrule
\midrule
keract & 1471 & 0.26 & 6.7\% & 482 & 0.72 & 20.0\% & 921 & 0.27 & 3.3\% \\
dtw & 866 & 0.55 & 0\% & 270 & 0.44 & 3.3\% & 713 & 0.46 & 27.7\% \\
notion-sdk-py & 196 & 0.60 & 13.3\% & 63 & 0.65 & 0\% & 52 & 0.44 & 13.9\% \\
atlassian- & \mr{2}{333} & \mr{2}{0.62} & \mr{2}{30.0\%} & \mr{2}{174} & \mr{2}{0.71}  & \mr{2}{13.3} & \mr{2}{106} & \mr{2}{0.74} & \mr{2}{3.5\%}  \\
python-api  &    &    &    &    &   &   &   &  &  \\
ESD & 1712 & 0.07 & 6.7\% & 720 & 0.08 & 13.3\% & 1013 & 0.06 & 6.7\% \\
Fiber & 458 & 0.64 & 23.3\% & 222 & 0.57 & 46.7\% & 320 & 0.81 & 20.0\% \\\midrule
\textbf{Mean} &  839.33 & 0.46 & 13.3\% & 321.83 & 0.53 & 16.1\% & 520.93 & 0.46 & 12.34\% \\
\textbf{Std.Dev.} &  628.80 & 0.24 & 11.4\% & 239.04 & 0.24 & 16.7\% & 417.50 & 0.28 & 9.57\% \\\bottomrule        
\end{tabular}
\end{table}

>>>>

%\begin{tabular}{l|r|rr|rr}
% ---------------- C++/Java/Rust table UM Only--------------------------
\begin{table}[hbtp]
\centering
%\captionsetup{justification=centering}
\footnotesize
\caption{Regex vs. Comby for C++ (top), Java (middle), and Rust (bottom). LOC describes the project files considered. Muts. is total number of mutants generated for those files. Invalid mutants are those that don't compile. Mut. Score refers to the Mutation Score.}
\label{tab:table_cpp1javarust}

@@

\begin{table}[hbtp]
\centering
\small 
\caption{Regex vs. Comby for Python. LOC describes the project files
  considered. Muts. is total number of mutants generated for those
  files.  Invalid mutants are ones that fail module load (e.g., due
  to imbalanced parenthesis, bad indentation, or similar problems).  We can use TCE to check for redundant Python mutants, shown under ``Red.''}
\label{tab:table_python1}
\begin{varwidth}{.9\columnwidth}
\begin{tabularx}{\linewidth}{l|r|rcrc|rcrc}
\toprule
\toprule
                 &                 & \multicolumn{4}{c|}{\textbf{Regex}}             &\multicolumn{4}{c}{\textbf{Comby}}  \\[1ex]
\textbf{Project} & \textbf{LOC}    & \textbf{Muts.} & \textbf{Red.}  & \textbf{\% Valid} & \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{Muts.} & \textbf{Red.}   &  \textbf{\% Valid} & \makecell{\textbf{Mut.} \\ \textbf{Score}}\\\midrule
keract           & 402             & 3984  & 729   & 41.53\% & 0.28           & 3067  & 533    & 47.96\%    & 0.26\\
dtw              & 118             & 2106  & 567   & 46.20\%    & 0.52           & 1835  & 639    & 47.19\%  & 0.55 \\
notion-          & \mr{2}{189}     & \mr{2}{1038}  & \mr{2}{82}    & \mr{2}{18.89\%}   & \mr{2}{0.57}         & \mr{2}{1019}  & \mr{2}{122}    & \mr{2}{19.23\%} & \mr{2}{0.60}  \\
sdk-py           & & & & & & \\[0.5ex]
atlassian-       & \mr{2}{236}      & \mr{2}{1511}  & \mr{2}{207}   & \mr{2}{19.99\%}    & \mr{2}{0.64}        & \mr{2}{1319}  & \mr{2}{351}    & \mr{2}{25.25\%} & \mr{2}{0.62}  \\
python-api       & & & & & & \\[0.5ex]
ESD              & 698             & 6268  & 1642  & 29.46\%    & 0.07           & 3874  & 614    & 44.18\% & 0.07\\
fiber            & 358             & 1565  & 163   & 31.08\% & 0.62           & 1466  & 241    & 31.24\% & 0.64\\\bottomrule
\end{tabularx}
\begin{tabularx}{\linewidth}{Xllrrrrc}
                  && &  \textbf{Red.}     & \textbf{Valid}  & \textbf{Invalid}  & \textbf{\% Valid} &\textbf{Mut. Score}\\\midrule
\multirow{4}{*}{\textbf{Overall}} & \multirow{2}{*}{Regex} & Mean &  565.00 & 913.00 & 1267.33 & 31.19\%  & 0.45\\
    &   &  Std.Dev. & 584.79  & 708.93 & 813.35 & 11.06\%  & 0.23\\\cline{2-8}
 & \multirow{2}{*}{Comby} & Mean & 416.67 & 839.33 & 840.67 & 35.84\% & 0.46\\
  &   &  Std.Dev. &  211.62 & 628.79 & 418.99 & 12.28\%  & 0.24 \\\bottomrule
\end{tabularx}
\end{varwidth}
\end{table}

@@

\begin{table}[htbp]
\centering
\caption{Python (Our Implementation vs. Mutmut vs. CosmicRay)}
\label{tab:table_python2}
\small
\begin{tabular}{l|rrr|rrr|rrr}
\toprule
                 & \mc{3}{c|}{\textbf{Comby}}   & \mc{3}{c|}{\textbf{Mutmut}} & \mc{3}{c}{\textbf{CosmicRay}} \\
\textbf{Project} & \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv}
& \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv} 
& \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv} \\ \midrule
\midrule
keract & 1471 & 0.26 & 6.7\% & 482 & 0.72 & 20.0\% & 921 & 0.27 & 3.3\% \\
dtw & 866 & 0.55 & 0\% & 270 & 0.44 & 3.3\% & 713 & 0.46 & 27.7\% \\
notion-sdk-py & 196 & 0.60 & 13.3\% & 63 & 0.65 & 0\% & 52 & 0.44 & 13.9\% \\
atlassian- & \mr{2}{333} & \mr{2}{0.62} & \mr{2}{30.0\%} & \mr{2}{174} & \mr{2}{0.71}  & \mr{2}{13.3\%} & \mr{2}{106} & \mr{2}{0.74} & \mr{2}{3.5\%}  \\
python-api  &    &    &    &    &   &   &   &  &  \\
ESD & 1712 & 0.07 & 6.7\% & 720 & 0.08 & 13.3\% & 1013 & 0.06 & 6.7\% \\
Fiber & 458 & 0.64 & 23.3\% & 222 & 0.57 & 46.7\% & 320 & 0.81 & 20.0\% \\\midrule
\textbf{Mean} &  839.33 & 0.46 & 13.3\% & 321.83 & 0.53 & 16.1\% & 520.93 & 0.46 & 12.34\% \\
\textbf{Std.Dev.} &  628.80 & 0.24 & 11.4\% & 239.04 & 0.24 & 16.7\% & 417.50 & 0.28 & 9.57\% \\\bottomrule        
\end{tabular}
\end{table}
